---
title: "Data Processing Kalauhaihai"
author: "Connor"
date: "5/17/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(lubridate)
library(readr)
```


#Reading in Data
As of May 25, 8 Data Files read in
  - 2 Conductivity
  - 2 Oxygen
  - 3 pH
  - 1 Temperature
  
```{r conductivity_kalauhaihai_garage_FebApr2023}
conductivity_kalauhaihai_garage_FebApr2023 <- read_csv(here("raw_data/kalauhaihai/data_conductivity_FebApr2023_KalauhaihaiGarage_21415543.csv"))
```

```{r conductivity_kalauhaihai_OctNov2022}
conductivity_kalauhaihai_OctNov2022 <- read_tsv(here("raw_data/kalauhaihai/data_conductivity_Kalauhaihai_Oct-Nov2022.txt"))
```

```{r oxygen_kalauhaihai_garage_FebApr2023}
oxygen_kalauhaihai_garage_FebApr2023 <- read_csv(here("raw_data/kalauhaihai/Data_oxygen_FebApr2023_KalauhaihaiGarage_21446085.csv"))
```

```{r oxygen_kalauhaihai_OctNov2022}
oxygen_kalauhaihai_OctNov2022 <- read_tsv(here("raw_data/kalauhaihai/data_oxygen_Kalauhaihai_Oct-Nov2022.txt"))
```

```{r pH_kalauhaihai_garage_FebApr2023}
pH_kalauhaihai_garage_FebApr2023 <- read_csv(here("raw_data/kalauhaihai/data_pH_FebApr2023_KalauhaihaiGarage_20839036.csv"))
```

```{r pH_kalauhaihai_OctNov2022}
pH_kalauhaihai_OctNov2022 <-
  read_tsv(here("raw_data/kalauhaihai/data_pH_Kalauhaihai_SN20839036_Oct-Nov2022.txt"))
```

```{r pH_kalauhaihai_Apr2022}
pH_kalauhaihai_Apr2022 <-
  read_tsv(here("raw_data/kalauhaihai/data_pH_Kalauhaihai_SN20839036_Apr2022.txt"), skip = 1)
```


```{r raw_temp_kalauhaihai_garage_Spring_2022}
raw_temp_kalauhaihai_garage_Spring_2022 <- read.csv(here("raw_data/kalauhaihai/data_temp_Kalauhaihai_Garage_Spring_2022.csv"), header = TRUE)
```
sets the first line as a header, Im not sure if this is truly needed. HOWEVER, I imported with the name raw_temp because the format is really weird. 

```{r temp_kalauhaihai_garage_Spring_2022}
temp_kalauhaihai_garage_Spring_2022 <- raw_temp_kalauhaihai_garage_Spring_2022[seq(2, nrow(raw_temp_kalauhaihai_garage_Spring_2022), by = 2), ]
```
This code skips every EVEN line. In the raw data, there was an empty line between each 
element. temp_kalauhaihai_garage_Spring_2022 is the main data set


#Data Cleaning 

```{r conductivity_kalauhaihai_garage_FebApr2023}
#Conductivity kalauhaihai, garage, FEB_APR 2023

# Clean Column Names


conductivity_kalauhaihai_garage_FebApr2023 <- conductivity_kalauhaihai_garage_FebApr2023 %>% 
  clean_names()


# Edit cleaned column names

colnames(conductivity_kalauhaihai_garage_FebApr2023)[which(names(conductivity_kalauhaihai_garage_FebApr2023) == "low_range_m_s_cm_lgr_s_n_21415543_sen_s_n_21415543")] <- "low_range_microSiemens"

colnames(conductivity_kalauhaihai_garage_FebApr2023)[which(names(conductivity_kalauhaihai_garage_FebApr2023) == "high_range_m_s_cm_lgr_s_n_21415543_sen_s_n_21415543")] <- "high_range_microSiemens"

colnames(conductivity_kalauhaihai_garage_FebApr2023)[which(names(conductivity_kalauhaihai_garage_FebApr2023) == "temp_c_lgr_s_n_21415543_sen_s_n_21415543")] <- "temp_celsius"

colnames(conductivity_kalauhaihai_garage_FebApr2023)[which(names(conductivity_kalauhaihai_garage_FebApr2023) == "date_time_gmt_10_00")] <- "date_time"


conductivity_kalauhaihai_garage_FebApr2023$date_time <- mdy_hms(conductivity_kalauhaihai_garage_FebApr2023$date_time)

# Select relevant columns 

conductivity_kalauhaihai_garage_FebApr2023 <- conductivity_kalauhaihai_garage_FebApr2023 %>% 
  select(date_time, low_range_microSiemens, high_range_microSiemens, temp_celsius)
```

```{r conductivity_kalauhaihai_OctNov2022}
#Combine Date and Time Column/// FIXED
#Conductivity kalauhaihai, OCT_NOV 2022

# Clean Column Names


conductivity_kalauhaihai_OctNov2022 <- conductivity_kalauhaihai_OctNov2022 %>% 
  clean_names()


# Edit cleaned column names

colnames(conductivity_kalauhaihai_OctNov2022)[which(names(conductivity_kalauhaihai_OctNov2022) == "low_range_m_s_cm_c_1_3")] <- "low_range_microSiemens"

colnames(conductivity_kalauhaihai_OctNov2022)[which(names(conductivity_kalauhaihai_OctNov2022) == "high_range_m_s_cm_c_1_3")] <- "high_range_microSiemens"

colnames(conductivity_kalauhaihai_OctNov2022)[which(names(conductivity_kalauhaihai_OctNov2022) == "temp_c_c_3")] <- "temp_celsius"

#Combine date and time columns
conductivity_kalauhaihai_OctNov2022 <- conductivity_kalauhaihai_OctNov2022 %>%
  unite(date_time, date, time, sep = " ")

#change class to charachter
conductivity_kalauhaihai_OctNov2022$date_time <- mdy_hms(conductivity_kalauhaihai_OctNov2022$date_time)

#Select Colums

conductivity_kalauhaihai_OctNov2022 <- conductivity_kalauhaihai_OctNov2022 %>% 
  select(date_time, low_range_microSiemens, high_range_microSiemens, temp_celsius)

```

```{r oxygen_kalauhaihai_garage_FebApr2023}
#Oxygen kalauhaihai, garage, FEB_APR 2023

#Clean Column Names
colnames(oxygen_kalauhaihai_garage_FebApr2023)[which(names(oxygen_kalauhaihai_garage_FebApr2023) == "DO conc, mg/L (LGR S/N: 21446085, SEN S/N: 21446085)")] <- "dissolved_oxygen_mg_l"

colnames(oxygen_kalauhaihai_garage_FebApr2023)[which(names(oxygen_kalauhaihai_garage_FebApr2023) == "Temp, °C (LGR S/N: 21446085, SEN S/N: 21446085)")] <- "temp_celsius"

colnames(oxygen_kalauhaihai_garage_FebApr2023)[which(names(oxygen_kalauhaihai_garage_FebApr2023) == "Date Time, GMT-10:00")] <- "date_time"

oxygen_kalauhaihai_garage_FebApr2023$date_time <- mdy_hms(oxygen_kalauhaihai_garage_FebApr2023$date_time)

#Select Columns
oxygen_kalauhaihai_garage_FebApr2023 <- oxygen_kalauhaihai_garage_FebApr2023 %>%
  select(date_time, dissolved_oxygen_mg_l, temp_celsius)
```

```{r oxygen_kalauhaihai_OctNov2022}
#Combine Date and Time Column/// FIXED
#Oxygen kalauhaihai, garage, OCT_NOV 2022

#Clean Column Names
colnames(oxygen_kalauhaihai_OctNov2022)[which(names(oxygen_kalauhaihai_OctNov2022) == "DO conc (mg/L) c:1 2")] <- "dissolved_oxygen_mg_l"

colnames(oxygen_kalauhaihai_OctNov2022)[which(names(oxygen_kalauhaihai_OctNov2022) == "Temp (°C) c:2")] <- "temp_celsius"

#Combine date and time columns
oxygen_kalauhaihai_OctNov2022 <- oxygen_kalauhaihai_OctNov2022 %>%
  unite(date_time, Date, Time, sep = " ")


oxygen_kalauhaihai_OctNov2022$date_time <- mdy_hms(oxygen_kalauhaihai_OctNov2022$date_time)
#Select Columns
oxygen_kalauhaihai_OctNov2022 <- oxygen_kalauhaihai_OctNov2022 %>%
  select(date_time, dissolved_oxygen_mg_l, temp_celsius)
```

```{r pH_kalauhaihai_Apr2022}
#pH, kalauhaihai, APR 2022
#date_time class is "dttm"

# Clean names

pH_kalauhaihai_Apr2022 <- pH_kalauhaihai_Apr2022 %>% 
  clean_names()

#Change column names

colnames(pH_kalauhaihai_Apr2022)[which(names(pH_kalauhaihai_Apr2022) == "p_h")] <- "pH"

colnames(pH_kalauhaihai_Apr2022)[which(names(pH_kalauhaihai_Apr2022) == "m_v")] <- "mv"

colnames(pH_kalauhaihai_Apr2022)[which(names(pH_kalauhaihai_Apr2022) == "temp_c")] <- "temp_celsius"

colnames(pH_kalauhaihai_Apr2022)[which(names(pH_kalauhaihai_Apr2022) == "date_time_gmt_1000")] <- "date_time"

pH_kalauhaihai_Apr2022$date_time <- mdy_hms(pH_kalauhaihai_Apr2022$date_time)

pH_kalauhaihai_Apr2022 <- pH_kalauhaihai_Apr2022 %>%
  select(date_time, temp_celsius, mv, pH)
```

```{r pH_kalauhaihai_garage_FebApr2023}
#pH, kalauhaihai, FEB_APR 2023

# Clean names

pH_kalauhaihai_garage_FebApr2023 <- pH_kalauhaihai_garage_FebApr2023 %>% 
  clean_names()

#Change column names

colnames(pH_kalauhaihai_garage_FebApr2023)[which(names(pH_kalauhaihai_garage_FebApr2023) == "ch_3_p_h_p_h")] <- "pH"

colnames(pH_kalauhaihai_garage_FebApr2023)[which(names(pH_kalauhaihai_garage_FebApr2023) == "ch_2_millivolts_mv")] <- "mv"

colnames(pH_kalauhaihai_garage_FebApr2023)[which(names(pH_kalauhaihai_garage_FebApr2023) == "ch_1_temperature_c")] <- "temp_celsius"

colnames(pH_kalauhaihai_garage_FebApr2023)[which(names(pH_kalauhaihai_garage_FebApr2023) == "date_time_hst")] <- "date_time"

pH_kalauhaihai_garage_FebApr2023$date_time <- mdy_hms(pH_kalauhaihai_garage_FebApr2023$date_time)

pH_kalauhaihai_garage_FebApr2023 <- pH_kalauhaihai_garage_FebApr2023 %>%
  select(date_time, temp_celsius, mv, pH)

```

```{r pH_kalauhaihai_OctNov2022}
#Combine Date and Time Column/// FIXED
#pH, kalauhaihai, OCT_NOV 2022

#Change column names

colnames(pH_kalauhaihai_OctNov2022)[which(names(pH_kalauhaihai_OctNov2022) == "pH c:4")] <- "pH"

colnames(pH_kalauhaihai_OctNov2022)[which(names(pH_kalauhaihai_OctNov2022) == "mV (mv) c:2")] <- "mv"

colnames(pH_kalauhaihai_OctNov2022)[which(names(pH_kalauhaihai_OctNov2022) == "Temp (°C) c:1")] <- "temp_celsius"

#Combine date and time columns
pH_kalauhaihai_OctNov2022 <- pH_kalauhaihai_OctNov2022 %>%
  unite(date_time, Date, Time, sep = " ")

pH_kalauhaihai_OctNov2022$date_time <- mdy_hms(pH_kalauhaihai_OctNov2022$date_time)

#Select Columns
pH_kalauhaihai_OctNov2022 <- pH_kalauhaihai_OctNov2022 %>%
  select(date_time, temp_celsius, mv, pH)

```

```{r temp_kalauhaihai_garage_Spring_2022}
#temp, kalauhaihai, garage, Spring 2022

#Change column names
temp_kalauhaihai_garage_Spring_2022 <- temp_kalauhaihai_garage_Spring_2022 %>% 
  clean_names()

colnames(temp_kalauhaihai_garage_Spring_2022)[which(names(temp_kalauhaihai_garage_Spring_2022) == "date_time_gmt_10_00")] <- "date_time"

colnames(temp_kalauhaihai_garage_Spring_2022)[which(names(temp_kalauhaihai_garage_Spring_2022) == "temp_c_lgr_s_n_20970094_sen_s_n_20970094")] <- "temp_celsius"


temp_kalauhaihai_garage_Spring_2022$date_time <- mdy_hms(temp_kalauhaihai_garage_Spring_2022$date_time)
#Select columns
temp_kalauhaihai_garage_Spring_2022 <- temp_kalauhaihai_garage_Spring_2022 %>% 
  select(date_time, temp_celsius)

```

